Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-01 PandaEvolution.tex
section 3. fixing definition of backfill. more to come in 4.

Titan’s backfill functionality offers the opportunity to avoid the overhead of
queue wait times without using pilot abstraction. Backfill availability is the
number of worker nodes that cannot be used for a certain amount of time by any
of the jobs already queued on Titan: All queued jobs are either too large or
their walltime is too long. At any point in time, Titan’s Moab scheduler can be
queried for backfill availability. Based upon the result of this query, a job
can be shaped to request no more than the backfill availability. As such, when
submitted this job is usually scheduled immediately, spending almost no time in
the queue.

@@

Usually, backfill availability is a fraction of the total capacity of the queue
but the size of Titan mitigates this limitation. Every year, about 10\% of
Titan's capacity remains unused, corresponding to an average of 30,000 unused
cores. This equals approximately 270M core hours per year, roughly 30\% of the
overall capacity of WLCG.

>>>>

% Titan’s backfill functionality offers the opportunity to avoid the overhead of
% queue wait times without using pilot abstraction. Backfill availability is the
% number of node-hours (or core-hours) that cannot be used for a certain amount
% of time by any of the jobs already queued on Titan: All queued jobs are either
% too large or their walltime is too long. At any point in time, Titan’s Moab
% scheduler can be queried for backfill availability. Based upon the result of
% this query, a job can be shaped to request no more than the backfill
% availability. As such, when submitted this job is usually scheduled
% immediately, spending almost no time in the queue.

Titan’s backfill functionality offers the opportunity to avoid the overhead of
queue wait times without using pilot abstraction. Backfill availability is the
number of node-hours (or core-hours) that  is not utilized by regular jobs
submitted to the queues on Titan. Titan’s backfill functionality offers the
opportunity to avoid the overhead of queue wait times without using pilot
abstraction.  It is important to note that backfill availability is  computed
retrospectively and is determined by Titan's operation team. Backfill
availability represents the theoretical maximum of node-hours that could be
utilized by ATLAS (or any other project) that submit under backfill mode.

@@

Backfill availability is typically a small fraction of the total capacity  of
a resource. Notwithstanding,  given the size of Titan this translates into a
substantial capacity. Every year, about 10\% of Titan's capacity remains
unused, corresponding to an average of 30,000 unused cores. This equals
approximately 270M core hours per year, roughly 30\% of the overall capacity
of WLCG.

### 2017-04-01 overall.tex
Shorter figure
refining subsection titles.
section 3. fixing definition of backfill. more to come in 4.

Currently, ATLAS deploys 20 instances of PanDA Broker on 4 Titan's DTNs, 5
instances per DTN. Each broker submits and manages the execution of 15 to 300
ATLAS jobs, one job for each worker node, and a theoretical maximum concurrent
use of 96,000 cores. Since November 2015, PanDA Brokers have operated only in
backfill mode, without a defined time allocation, and running at the lowest
priority on Titan.

We evaluate the efficiency, scalability and reliability of the PanDA Brokers
along two dimensions: (i) the amount of backfill availability utilized by the
PanDA Brokers; and (ii) the amount of runtime spent performing detector
simulations. We based these evaluations on measuring the number of cores
utilized by ATLAS on Titan, the overall backfill availability, the number of
detector simulations performed on all the resources available to ATLAS and on
Titan, and the failure rate of these simulations. All the measurements were
performed between January 2016 and February 2017, hereafter called `experiment
time window'.

% -----------------------------------------------------------------------------
\subsection{Utilization and Efficiency of PanDA Broker on Titan}
\label{ssec:panda_titan}

@@

% -----------------------------------------------------------------------------
\subsection{Efficiency, Scalability, and Reliability of Detector Simulation on Titan}
\label{ssec:panda_titan}

@@

% -----------------------------------------------------------------------------
\subsection{PanDA I/O Impact at OLCF}

>>>>

Currently, ATLAS deploys 20 instances of the PanDA Broker on 4 Titan's DTNs, 5
instances per DTN. Each broker submits and manages the execution of 15 to 300
ATLAS jobs, one job for each worker node, and a theoretical maximum concurrent
use of 96,000 cores. Since November 2015, PanDA Brokers have operated only in
backfill mode, without a defined time allocation, and running at the lowest
priority on Titan.

We evaluate the efficiency, scalability and reliability of the PanDA Brokers
along two dimensions: (i) backfill utilization by the
PanDA Brokers; and (ii) the amount of runtime spent performing detector
simulations. We based these evaluations on measuring the number of cores
utilized by ATLAS on Titan, the overall backfill availability, the number of
detector simulations performed on all the resources available to ATLAS and on
Titan, and the failure rate of these simulations. All the measurements were
performed between January 2016 and February 2017, hereafter called `experiment
time window'.

% -----------------------------------------------------------------------------
\subsection{Characterizing the PanDA Broker on Titan}
\label{ssec:panda_titan}

@@

% -----------------------------------------------------------------------------
\subsection{Characterizing the Detector Simulation on Titan}
\label{ssec:panda_titan}

@@

% -----------------------------------------------------------------------------
\subsection{Characterizing PanDA I/O}
